---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  ---
  
  ```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>",
fig.width = 7,
fig.height = 6,
echo=FALSE,
warnings=FALSE,
message = FALSE
)
```

```{r setup}
library(Casanova)
library(tidyverse)
library(nlstools)
library(nleqslv)
library(deSolve)
library(doParallel)
library(foreach)
library(ggplot2)
library(gridExtra)
```

## Read in DSD Data 



### Read in Hard-coded Nozzle and DDD params

```{r}

## Load hard-coded inputs

Nozzle_params <- as_tibble(read.csv("./../data-raw/Nozzle_Params.csv", header = T))
DDD_params <- as_tibble(read.csv("../data-raw/DDD_Params.csv", header = T))
p <- Nozzle_params %>% select(p)
NF <- Nozzle_params %>% select(NF)
ddd1 <- DDD_params$ddd1
ddd2 <- DDD_params$ddd2
ddd3 <- DDD_params$ddd3
```


```{r include=FALSE}
library(Casanova)
library(tidyverse)

dsdFile <- read_csv("DSD_ Xtendimax _ AI11004 .csv")
dsdFile <- dsdFile%>% mutate(ymean=(Trial_1+Trial_2+Trial_3)/3)

## Determine where to draw the cut-off (begin with first value over zero and end with first value that reaches 100)
firsty <- min(which(dsdFile$ymean > 0))
lasty <- max(which(dsdFile$ymean < 100)) + 1

y <-  dsdFile$ymean %>%
  tibble::enframe() %>%
  slice(firsty:lasty) %>%
  pull(value)
Dpdata <- dsdFile$Droplet_Size_microns%>%tibble::enframe() %>%
  slice(firsty:lasty) %>%
  pull(value)
pars <- psd(y,Dpdata)

source("DefaultInputs.R")
```

```{r}
pars$plot
```


```{r}
knitr::kable(pars$table, caption="PSD Curve Fitting Parameters")
```




### Part 2: Wet Bulb Calculation

```{r}
Twb <- wet_bulb(Tair, Patm, RH)

```

Change in Wet Bulb Temperature (DTwb): `r Twb[1]`

Wet Bulb Temperature (Twb): `r Twb[2]`

### Part 3: Wind Profile Calculation



```{r}
wv <- WV2m (z1=z1, z2, ux1, ux2)
z0 <- wv[1]
Uf <- wv[2]
# Friction height, cm (z0): 0.33
# Friction velocity, cm/sec (uf): 33.53
```

-  Friction height, cm (z0): `r wv[1]`

- Friction velocity, cm/sec (uf): `r wv[2]`

### Part 4: Droplet Transport Calculation


```{r}
charac<-charact_cal(app_p,angle, rhosoln) 
charac
```


```{r include=F}
DTwb<-Twb[1] # Wetbulb temperature depression, C
print("Solving Straight Down Problem")
droplet_1<-droplet_transport(Tair,RH,rhow,rhos,xs0,H0,DTwb,hcm,Uf,z0,app_p,charac[1],charac[2],ddd1,"Silent")
print("Solving with Wind Problem")
droplet_2<-droplet_transport(Tair,RH,rhow,rhos,xs0,H0,DTwb,hcm,Uf,z0,app_p,charac[3],charac[4],ddd2,"text")
print("Solving against Wind Problem")
droplet_3<-droplet_transport(Tair,RH,rhow,rhos,xs0,H0,DTwb,hcm,Uf,z0,app_p,charac[5],charac[6],ddd3,"Silent")

print("Finished Solving for Droplet Transport")

```

- Plot the droplet data

```{r}
droplet1_data <- as_tibble(droplet_1) %>%
  mutate(Droplet = "Centerline",
         ColorSet = "#ffd700")
droplet2_data <- as_tibble(droplet_2) %>%
  mutate(Droplet = "Downwind",
         ColorSet = "#00ffd7")
droplet3_data <- as_tibble(droplet_3) %>%
  mutate(Droplet = "Upwind",
         ColorSet = "#d700ff")

All_droplet_data <- rbind(droplet1_data,
                          droplet2_data,
                          droplet3_data)

droplet_plot <- ggplot(All_droplet_data, aes(x = Xdist, y = Dp.1.23., color = Droplet)) +
  geom_point(size = 3, alpha = 0.5) +
  scale_color_manual(values = c("#ffd700", "#00ffd7", "#d700ff")) +
  ylab("Initial Droplet Diameter (microns)") +
  xlab("Distance Traveled to Depositions from Nozzle Centerline (ft)") +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    legend.background = element_rect(fill=alpha('white', 0.4)),
    legend.position = "right",
    legend.text = element_text(size = 16),
    axis.line = element_line(colour = "black"),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    axis.title.y = element_text(size = 16, vjust= 1.5),
    axis.title.x = element_text(size = 16)
  )

droplet_plot
```


```{r}
names(All_droplet_data)[1:3] <- c("Droplet_diameter","Distance_traveled","Droplet")
knitr::kable(All_droplet_data[,1:3])
```


### Part 5: Deposition with Distance


```{r}

# Part 5
# ________________________________________
a<-unname(pars$res)  # Calibration from step #1 (removing the stored names)

# Input from previous function
Cent<-droplet_1[2]$Xdist
Dwnd<-droplet_2[2]$Xdist
Uwnd<-droplet_3[2]$Xdist

deposition<-deposition_calcs(IAR,xactive,FD,PL, NozzleSpacing, psipsipsi,rhoL, Cent,Dwnd,Uwnd, Dpmax, DDpmin,a,MMM, lambda,"Silent")
deposition$dep_plot
###################
tibble(Distance = deposition$XX,
       Deposition = deposition$APplume) %>%
  knitr::kable()
```


### Part 6: Generate Report


- use parameterized reporting tool!

